Usage metrics

### 2020-12-16 analysis/usage.Rmd

nb_runs <- E %>%
  pull(file) %>%
  n_distinct()
overview_table(
  r("Corpus",corpus_size),
  r("Nbruns", nb_runs)
) 
```

@@

@@

tmp <- sites_per_variant %>% filter(ev_variant == "eval")
dyn_evl <- if (nrow(tmp)==0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "evalq")
dyn_evq <- if (nrow(tmp) == 0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "eval.parent") 
dyn_evalp <- if(nrow(tmp) == 0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "local")
dyn_lol <- if(nrow(tmp) == 0) { 0 } else { tmp$n }

>>>>

nb_runs <- E %>%
  pull(file) %>%
  n_distinct()
overview_table(
  r("Corpus", corpus_size),
  r("NbRuns", nb_runs)
) 
```

@@

Here we compute the number of static call sistes to eval to compare it with
the number of call sites with triggered dynamically. The former is larger
than the latter because code coverage is not perfect.

@@

tmp <- sites_per_variant %>% filter(ev_variant == "eval")
dyn_evl <- if (nrow(tmp)==0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "evalq")
dyn_evq <- if (nrow(tmp) == 0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "eval.parent") 
dyn_evp <- if(nrow(tmp) == 0) { 0 } else { tmp$n }
tmp <- sites_per_variant %>% filter(ev_variant == "local")
dyn_loc <- if(nrow(tmp) == 0) { 0 } else { tmp$n }
